### 2005-11-11 doc/EFA/efa.tex
*** empty log message ***

\noindent Now consider the action function $a^{(A\|A')\|A''} : X^c
\rightarrow X^c$.

>>>>

\noindent Now consider the action function $a^{(A\|A')\|A''} : X^c
\rightarrow X^c$.
\subsection{The translation of an EFA to  a FA}
To simplify the realization we shall restrict us to quite simple
action- and guard functions. For the updating functions we assume
that $a_{q \sigma}(x)=(a^1_{q \sigma}(x),...,a^n_{q
\sigma}(x))=(a^1_{q \sigma}(x_1),...,a^n_{q \sigma}(x_n))$. In
other words, the updating of the variables are independent from
each other. For the guard functions we assume that they have the
following form $g_{q \sigma}(x)=g^1_{q \sigma}(x_1)\wedge
...\wedge g^n_{q \sigma}(x_n)$. These assumptions makes straight
forward to translate an EFA to a FA.

-realize an automata for each variable.
